---
title: "Hour Record"
description: |
  Article about the development of the cycling hour record
author: "Julian During"
date: "4 11 2021"
output: html_document
repository_url: https://github.com/duju211/pin_strava
creative_commons: CC BY
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
source("libraries.R")

Sys.setenv("RSTUDIO_VERSION" = '1.4.1725')
```

# Idea

Visualise the development of the cycling hour record.
It is a record attempt of cyclyst, who try to cover the longest possible
distance in one hour. Since 2014 there are unified rules for the hour record.
Since then there were 6 different record holders. Explore how these records
compare to each other.

The analysis is realised in a target plan. Look at the graph representation of
this plan:

```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
graph_net <- tar_visnetwork(reporter = "silent")
```

```{r, echo=FALSE}
graph_net
```

# Data

Get the data from the following urls:
`r glue_collapse(tar_read(rel_urls), sep = ", ")`

Map over the different urls and save the data along with the url adress:

```{r, code=read_lines("R/time_splits_raw.R")}
```

```{r, echo=FALSE}
tar_read(df_time_splits_raw)
```

Preprocessing of the raw data. Extract the rider name and preprocess the kpi
columns.

```{r, code=read_lines("R/time_splits.R")}
```

```{r, echo=FALSE}
tar_read(df_time_splits)
```

# Visualisation

Plot the development of the average speeds. Differentiate the riders by color:

```{r, code=read_lines("R/vis_average_speed.R")}
```

```{r, echo=FALSE}
tar_read(gg_average_speed)
```

